---
title: Reproducible Research Project 2"
output: html_document
---
## Synopsis
The project will figure out these questions:

1.Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

2.Across the United States, which types of events have the greatest economic consequences?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data Processing

```{r}
library(dplyr)

StormData <- read.csv(bzfile("repdata-data-StormData.csv.bz2"))
fatalities <- StormData %>% select(EVTYPE, FATALITIES) %>% group_by(EVTYPE) %>% summarise(total.fat = sum(FATALITIES)) %>% arrange(-total.fat)
injuries <- StormData %>% select(EVTYPE, INJURIES) %>% group_by(EVTYPE) %>% summarise(total.inj= sum(INJURIES)) %>% arrange(-total.inj)

damage <- StormData %>% select(EVTYPE, PROPDMG,PROPDMGEXP,CROPDMG,CROPDMGEXP)

Symbol <- sort(unique(as.character(damage$PROPDMGEXP)))
Multiplier <- c(0,0,0,1,10,10,10,10,10,10,10,10,10,10^9,10^2,10^2,10^3,10^6,10^6)
convert.Multiplier <- data.frame(Symbol, Multiplier)

damage$Prop.Multiplier <- convert.Multiplier$Multiplier[match(damage$PROPDMGEXP, convert.Multiplier$Symbol)]
damage$Crop.Multiplier <- convert.Multiplier$Multiplier[match(damage$CROPDMGEXP, convert.Multiplier$Symbol)]

damage <- damage %>% mutate(PROPDMG = PROPDMG*Prop.Multiplier) %>% mutate(CROPDMG = CROPDMG*Crop.Multiplier) %>% mutate(TOTAL.DMG = PROPDMG+CROPDMG)

damage.total <- damage %>% group_by(EVTYPE) %>% summarize(TOTAL.DMG.EVTYPE = sum(TOTAL.DMG))%>% arrange(-TOTAL.DMG.EVTYPE) 

```



## Results
We will see three plots about events on population health and economic

```{r}
library(ggplot2)

ggplot(fatalities[1:10,], aes(x=reorder(EVTYPE, -total.fat), y=total.fat))+
  geom_bar(stat="identity",fill="steel blue") + 
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=1))+
  ggtitle("Events with Highest Total Fatalities") +
  labs(x="EVENT TYPE", y="Total Fatalities")

ggplot(injuries[1:10,], aes(x=reorder(EVTYPE, -total.inj), y=total.inj))+
  geom_bar(stat="identity",fill="steel blue") + 
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=1))+
  ggtitle("Events with Highest Total Injuries") +
  labs(x="EVENT TYPE", y="Total Injuries")

ggplot(damage.total[1:10,], aes(x=reorder(EVTYPE, -TOTAL.DMG.EVTYPE), y=TOTAL.DMG.EVTYPE))+
  geom_bar(stat="identity",fill="steel blue") + 
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=1))+
  ggtitle("Top 10 Events with Highest Economic Impact") +
  labs(x="EVENT TYPE", y="Total Economic Impact ($USD)")

```
