---
title: "Untitled"
output: html_document
---
## Part 2: Basic Inferential Data Analysis
1.Load the ToothGrowth data and perform some basic exploratory data analyses

2.Provide a basic summary of the data.

3.Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

4.State your conclusions and the assumptions needed for your conclusions.

```{r}
data("ToothGrowth")
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
ggplot(aes(x=dose, y=len), data=ToothGrowth) + 
  geom_boxplot() +
  xlab("Dose Amount") + 
  ylab("Tooth Length") + 
  facet_grid(.~ supp) +
  ggtitle("Tooth Length vs. Dose Amount") + 
  theme(plot.title = element_text(lineheight=.8, face="bold"))

summary(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)

t.test(len~supp,data=ToothGrowth)

```

Since the p-value is 0,06 and the confidence interval of the test contains zero we can say that supplement types seems to have no impact on Tooth growth based on this test.

```{r}
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(0.5,2.0))
t.test(len~dose,data=ToothGrowth_sub)
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,2.0))
t.test(len~dose,data=ToothGrowth_sub)
```

Since p-value of both test is 0 and the CI does not include 0, we can reject the null hypothesis.

## Conclusion:
Assumptions:The distribution of the sample means follows the Central Limit Theorem.

From the t test, we can conclude that supplement delivery method has no effect on tooth growth/length, however, increasing in dose will have a longer tooth length.